---
output:
  github_document:
    html_preview: false
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="README-"
)
```


## Context

`"BinDist"` is a package that implements the relevant calculations and parameters necessary to calculate the Binomial distribution of discrete random variables, as well as further implementations of the cumulative binomial distribution and relevant visuals.


+ `bin_choose()` computes the combinations of size k that can be selected from size n, order doesn't matter  
+ `bin_probability()` computes the binomial probability of k successes from n trials, with a certain probability of success  
+ `bin_distribution()` compiles the binomial probability of varying successes to form a binomial probability distribution  
+ `bin_cumulative()` compiles the cumulative binomial probability to form the cumulative provavility distribution  
+ `plot()` plots the distribution of `bin_distribution()` and `bin_cumulative()`  
+ `bin_variable()` displays the parameters of the binomial distribution  
+ `summary()` applied onto `bin_variable()` displays the summary measures of the distribution


***

###Install the Package

Utilize the package `"devtools"` to install the package:

```{r}
# install.packages("devtools")

# install "BinDist" without vignettes
devtools::install_github("angglez/binomial")

# install "BinDist" with vignettes
devtools::install_github("angglez/binomial", build_vignettes=TRUE)
```


***

###Application

```{r, fig.show='hold'}
library(BinDist)

#table of binomial probability distribution and cumulative probability distribution
dis2 <- bin_cumulative(10,0.3)
dis2

#graph of binomial probability distribution
dis1 <- bin_distribution(10,0.3)
plot(dis1)

#graph of cumulative binomial probability distribution
plot(dis2)

#display of binomial distribution variables and summary measures
sum <- bin_variable(10,0.3)
summary(sum)
```

